Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2022-09-09 inst/skeleton/ms.Rmd
more messing with and such and things of this nature, if you will
scrub src/ dir, add targets compatability, add ms.yaml, and more stuff.

---
title: "Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/steveproj). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com. Carl Sagan has regrettably not been with us for 25 years and this tutorial is so beneath someone of his stature."
author:
- name: Carl Sagan
  affiliation: Cornell University & the Cosmos
- name: Steven V. Miller
  affiliation: Clemson University
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
bibliography: inst/refs.bib
abstract: "Gathered by gravity rings of Uranus finite but unbounded extraordinary claims require extraordinary evidence permanence of the stars white dwarf. A mote of dust suspended in a sunbeam invent the universe rich in heavy atoms hearts of the stars vastness is bearable only through love at the edge of forever. Something incredible is waiting to be known descended from astronomers bits of moving fluff vanquish the impossible with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena and billions upon billions upon billions upon billions upon billions upon billions upon billions."
keywords: "R Markdown, R, Make, {stevetemplates}, the Cosmos, billions and billions"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
header-includes:
  - \usepackage{longtable}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
---

@@

\vspace{.5cm}
\begin{hypothesis}
\begin{minipage}[t]{5.1 in}
This is a hypothesis, but only for LaTeX. MS Word will pass over it like a good boy, as will HTML. Mercifully, neither has any concept of LaTeX code and will ignore it upon seeing it. To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field. This will have to do.
\end{minipage}
\end{hypothesis}
\vspace{.5cm}

@@

White dwarf courage of our questions cosmic ocean gathered by gravity Jean-François Champollion science. Are creatures of the cosmos another world extraordinary claims require extraordinary evidence from which we spring vastness is bearable only through love at the edge of forever. Sea of Tranquility descended from astronomers descended from astronomers not a sunrise but a galaxyrise concept of the number one not a sunrise but a galaxyrise? Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence. Here's Table \@ref(tab:tab-reg).

```{r tab-reg}

@@

modelsummary(Mods, output=table_format,
             title = "A Regression Model Full of Goodness",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$",
             coef_map = c("agea" = "Age", 
                          "female" = "Female", 
                          "eduyrs" = "Education (in Years)",
                          "uempla" = "Unemployed", 
                          "hinctnta" = "Household Income (Deciles)", 
                          "lrscale" = "Ideology (L to R)", 
                          "noise" = "Stupid Noise Variable",
                          "(Intercept)" = "Intercept"),
             align=c("lcc")) -> tab_reg

if (!is_docx) {
  tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
} else {
  tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
} 
```

@@

Descended from astronomers laws of physics vastness is bearable only through love something incredible is waiting to be known invent the universe rings of Uranus. From which we spring inconspicuous motes of rock and gas a very small stage in a vast cosmic arena permanence of the stars intelligent beings gathered by gravity? Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword. Here's Figure \@ref(fig:fig-sims).

```{r fig-sims, fig.cap="Simulated Immigration Sentiment by Ideology"}

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)")

@@

@@

<!-- This option seems to be more pleasing for rmarkdown::pdf_document() with my templates -->
<!-- \setlength{\parskip}{6pt} -->

<!-- If you're using bookdown, this seems to look better with bookdown::pdf_document2() -->
\setlength{\parskip}{8pt}
\setlength{\parindent}{-0.15in}
\setlength{\leftskip}{0.15in}
\vspace*{-0.35in}
\noindent
\singlespacing

>>>>

@@

<!-- \vspace{.5cm} -->
<!-- \begin{hypothesis} -->
<!-- \begin{minipage}[t]{5.1 in} -->
<!-- This is a hypothesis, but only for LaTeX. MS Word will pass over it like a good boy, as will HTML. Mercifully, neither has any concept of LaTeX code and will ignore it upon seeing it. To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field. This will have to do. -->
<!-- \end{minipage} -->
<!-- \end{hypothesis} -->
<!-- \vspace{.5cm} -->

@@

White dwarf courage of our questions cosmic ocean gathered by gravity Jean-François Champollion science. Are creatures of the cosmos another world extraordinary claims require extraordinary evidence from which we spring vastness is bearable only through love at the edge of forever. Sea of Tranquility descended from astronomers descended from astronomers not a sunrise but a galaxyrise concept of the number one not a sunrise but a galaxyrise? Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence.

```{r make-table}

@@

modelsummary(Mods, output=table_format,
             title = "A Regression Model Full of Goodness",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$",
             coef_map = c("agea" = "Age", 
                          "female" = "Female", 
                          "eduyrs" = "Education (in Years)",
                          "uempla" = "Unemployed", 
                          "hinctnta" = "Household Income (Deciles)", 
                          "lrscale" = "Ideology (L to R)", 
                          "noise" = "Stupid Noise Variable",
                          "(Intercept)" = "Intercept"),
             align=c("lcc")) -> tab_reg
```

```{r tab-reg-latex, eval=is_latex}
tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
```

```{r tab-reg-docx, eval=is_docx}
# flextable would be nicer, but no real add_rows support here.
# tab_reg %>%
#   flextable::fontsize(size=10, part="all") %>%
#   flextable::font(fontname = "Palatino", part="all") %>%
#   flextable::padding(padding=1) %>%
#   #flextable::add_body() %>%
#   flextable::autofit()
# #

tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
```

@@

Descended from astronomers laws of physics vastness is bearable only through love something incredible is waiting to be known invent the universe rings of Uranus. From which we spring inconspicuous motes of rock and gas a very small stage in a vast cosmic arena permanence of the stars intelligent beings gathered by gravity? Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword.

```{r make-sims-ideology}

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims

@@

```{r fig-sims-ideology-latex, eval=is_latex, fig.cap="Simulated Immigration Sentiment by Ideology"}
fig_sims
```

```{r fig-sims-ideology-docx, eval=is_docx, fig.cap="Simulated Immigration Sentiment by Ideology", dev='png', dpi=600}
fig_sims
```

@@
